Domain-Driven Generative Data Model for BigPetStore

### 2014-07-16 bdcloud_paper/latex/paper.tex
Added description of HMM observable probabilities

\section{Overview of Models \& Simulations}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.75in]{figures/transaction_simulation.eps}
  \caption{Flowchart of Transaction Monte Carlo Simulation}
  \label{fig:trans_sim}
\end{figure}

@@

\begin{align}
&\beta_c \sim \text{U}(a, b) \\
&T_{O, i} \sim \text{Exp}(\beta^{-1}_c) \\
&T_{P, i} = T_{E,i} - T_{P, i} \\
&T_T = \min_i \, \{  T_{P, i}\}
\end{align}

@@

\begin{figure*}[!t]
  \centering
  \includegraphics[width=6in]{figures/shopping_cart_simulation.eps}
  \caption{Shopping Cart Hidden Markov Model}
  \label{fig:shopping_cart_sim}
\end{figure*}

@@

A customer’s purchases in each transaction are modeled using a layered Hidden Markov Model (HMM) (Figure~\ref{fig:shopping_cart_sim}).  The HMM has three states: the start state, the purchase states, and the stop state. There are an infinite number of purchase states, identified by the exhaustion times of the customer's item categories, the transaction time, and the number of items purchased in the current transaction. The observables of the purchase states correspond to the item categories and are Markov models for choosing the item to be purchased from the category. The observables are \textcolor{red}{assigned probabilities} based on the amounts of time (based on the usage simulations) until the customer uses the remaining amount of each item category.

>>>>

\section{Overview of Model \& Simulation Procedures}

\textcolor{red}{need an intro paragrpah}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.5in]{figures/transaction_simulation.eps}
  \caption{Flowchart of Transaction Monte Carlo Simulation}
  \label{fig:trans_sim}
\end{figure}

@@

\begin{align}
&\beta_c \sim \text{U}(a, b) \\
&T_{O, i} \sim \text{Exp}(\beta^{-1}_c) \\
&T_{P, i} = T_{E,i} - T_{O, i} \\
&T_T = \min_i \, \{  T_{P, i}\}
\end{align}

@@

\begin{figure*}[!t]
  \centering
  \includegraphics[width=6in]{figures/shopping_cart_simulation.eps}
  \caption{Example Shopping Cart Hidden Markov Model}
  \label{fig:shopping_cart_sim}
\end{figure*}

@@

A customer's purchases in each transaction are modeled using a layered Hidden Markov Model (HMM) (Figure~\ref{fig:shopping_cart_sim}).  The HMM has three states: the start state, the purchase states, and the stop state. There are an infinite number of purchase states, identified by the exhaustion times of the customer's item categories, the transaction time, and the number of items purchased in the current transaction. The observables of the states correspond to the item categories.  Each item category $i$ is assigned a weight $w_i$ according to the amount of time between the transaction time $T_t$ and $T_{E,i}$ when each item category will be exhausted (based on the usage simulations):

\begin{equation}
w_i = - \lambda_i \exp(-\lambda_i (T_{E, i}- T_{T}))
\end{equation}

The probability $p(X=i)$ of choosing item category $i$ is given by the normalizing the weight $w_i$ by the sum of all of the weights $W$:

\begin{align}
&p(X=i) = W^{-1} w_i \\
&W = \sum_i w_i \nonumber
\end{align}

The item category for the purchase is chosen using a Roulette Wheel sampler.
